### 2010-09-23 trunk/paper/IIWAS2010/content/results_discussion.tex
updated to the paper

Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task. Topic modeling provides a promising approach to identifying pages relevant to a given class in a more automated manner \cite{Blei2003latentdirichlet}. We believe a mix between our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results. Combining this with the method of Elmeleegy et al. \cite{1687749} may completely remove the user from the answer path generation process.

>>>>

%Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task. 
Topic modeling provides a promising approach to identifying pages relevant to a given class in a more automated manner. We believe a mix between our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results. Combining this with the method of Elmeleegy et al. \cite{1687749} may completely remove the user from the answer path generation process.
